Paper Figures and Text

### 2023-01-20 Fish Data Analysis/Final_Plots.Rmd
Ran code to make the 3D data files

>>>>

```{r}
ggplot(school_data %>% filter(Flow == "Still Water"), 
       aes(x = NND, y = Area, color = interaction(Ablation,Darkness,sep=", ")))+
  geom_point()+
  #geom_smooth(method = "glm", formula = 'y ~ poly(x, 2)', se = FALSE)+
  geom_smooth(method = "gam", se = FALSE)+
  theme_classic()+
  guides(color = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("NND (BL)")+
  ylab("Area (BL^2)")

## Velocity Correlations

```{r}
raw_comp_data <- read.csv("Data/Fish_Comp_Values.csv")
raw_comp_data <- na.omit(raw_comp_data)

comp_data <- raw_comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           select(-X)

velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10) %>% filter(Fish1_Speed < 5) %>% filter(Fish2_Speed < 5)  %>% filter(Flow == "Still Water")

velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,1))) %>% filter(round_Distance != 8)

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,0.1))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
                                                         mean_Spatial_Auto = mean(Spatial_Auto),
                                                         sd_Spatial_Auto = sd(Spatial_Auto),
                                                         count = n()) %>%
                                               ungroup() %>%
                                               mutate(round_Distance = as.numeric(levels(round_Distance))[round_Distance]) %>%
                                               filter(count > 5)
```

```{r}
ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none") +
  ylab("Correlation Strength")+
  xlab("Distance (BL)")

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_smooth(method = "glm", se = FALSE, color = "black")+
  #geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
  #              position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  facet_wrap(~Flow_Ablation_Darkness)+
  theme_classic()
```

ggplot(velocity_cor_data, aes(x = Fish1_Speed, y = Fish2_Speed))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = "lm")+
  theme_classic()+ 
  theme(legend.position = "none")

ggplot(velocity_cor_data, aes(x = Distance, y = Fish1_Speed*Fish2_Speed))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none")

cor.test(velocity_cor_data$Fish1_Speed,velocity_cor_data$Fish2_Speed)

ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff), 
                                                                color = Flow_Ablation_Darkness))+
  geom_violin()+
  theme_classic()

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Speed_Diff, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_errorbar(aes(ymin = mean_Speed_Diff-sd_Speed_Diff, ymax = mean_Speed_Diff+sd_Speed_Diff),
                position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_classic()

speed_diff_glm <- glm(Speed_Diff ~ round_Distance * Flow_Ablation_Darkness, data = velocity_cor_data)
Anova(speed_diff_glm)

#emmeans(speed_diff_glm, specs = pairwise ~ Flow_Ablation_Darkness)
#emmeans(speed_diff_glm, specs = pairwise ~ round_Distance)

### 2023-01-20 Fish Data Analysis/Paper_Figures.qmd
Ran code to make the 3D data files

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
                           ungroup()
```

@@

area_still
area_flow
```

```{r}
ggplot(school_data %>% filter(Flow == "Still Water"), 
       aes(x = NND, y = Area, color = interaction(Ablation,Darkness,sep=", ")))+
  geom_point()+
  #geom_smooth(method = "glm", formula = 'y ~ poly(x, 2)', se = FALSE)+
  geom_smooth(method = "gam", se = FALSE)+
  theme_classic()+
  guides(color = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("NND (BL)")+
  ylab("Area (BL^2)")

### Now we combine them

```{r}
school_stats_mega_plot <- ggarrange(nnd_still, nnd_flow, 
                                    polar_still, polar_flow,
                                    speed_still, speed_flow,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 2, nrow = 3)

ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 20)
```

## Velocity Correlations

```{r}
raw_comp_data <- read.csv("Data/Fish_Comp_Values.csv")
raw_comp_data <- na.omit(raw_comp_data)

comp_data <- raw_comp_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                             mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                             mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                             mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           select(-X)

velocity_cor_data <- comp_data %>% filter(abs(Speed_Diff) < 10) %>% filter(Fish1_Speed < 5) %>% filter(Fish2_Speed < 5)  %>% filter(Flow == "Still Water")

velocity_cor_data <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,1))) %>% filter(round_Distance != 8)

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,0.1))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
                                                         mean_Spatial_Auto = mean(Spatial_Auto),
                                                         sd_Spatial_Auto = sd(Spatial_Auto),
                                                         count = n()) %>%
                                               ungroup() %>%
                                               mutate(round_Distance = as.numeric(levels(round_Distance))[round_Distance]) %>%
                                               filter(count > 5)
```

```{r}
ggplot(velocity_cor_data, aes(x = Distance, y = Spatial_Auto))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none") +
  ylab("Correlation Strength")+
  xlab("Distance (BL)")

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_smooth(method = "glm", se = FALSE, color = "black")+
  #geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
  #              position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  facet_wrap(~Flow_Ablation_Darkness)+
  theme_classic()
```

ggplot(velocity_cor_data, aes(x = Fish1_Speed, y = Fish2_Speed))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = "lm")+
  theme_classic()+ 
  theme(legend.position = "none")

ggplot(velocity_cor_data, aes(x = Distance, y = Fish1_Speed*Fish2_Speed))+
  geom_point(alpha = 0.1)+
  theme_classic()+ 
  theme(legend.position = "none")

cor.test(velocity_cor_data$Fish1_Speed,velocity_cor_data$Fish2_Speed)

ggplot(velocity_cor_data %>% filter(Flow == "Still Water"), aes(x = factor(round_any(Distance,2)), y = abs(Speed_Diff), 
                                                                color = Flow_Ablation_Darkness))+
  geom_violin()+
  theme_classic()

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Speed_Diff, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_errorbar(aes(ymin = mean_Speed_Diff-sd_Speed_Diff, ymax = mean_Speed_Diff+sd_Speed_Diff),
                position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_classic()

speed_diff_glm <- glm(Speed_Diff ~ round_Distance * Flow_Ablation_Darkness, data = velocity_cor_data)
Anova(speed_diff_glm)

#emmeans(speed_diff_glm, specs = pairwise ~ Flow_Ablation_Darkness)
#emmeans(speed_diff_glm, specs = pairwise ~ round_Distance)

>>>>

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups)) %>%
                           ungroup()
```

@@

area_still
area_flow
```
### Number of Groups

group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Groups,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Groups_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Groups_Mean_Val-Area_SD_Val, ymax=Groups_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Number of Groups") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Groups,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Groups_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Groups_Mean_Val-Groups_SD_Val, ymax=Groups_Mean_Val+Groups_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Number of Groups") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

group_still
group_flow
```
### Now we combine them

```{r}
school_stats_mega_plot <- ggarrange(nnd_still, nnd_flow, 
                                    polar_still, polar_flow,
                                    speed_still, speed_flow,
                                    group_still, group_flow,
          labels = c("A", "B", "C", "D", "E", "F", "G", "H"),
          ncol = 2, nrow = 4)

ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 30)
```
